Parsing medial prefrontal cortex: A joint meta-analytic and graph-theoretic approach.

### 2018-08-28 Manuscript/Manuscript.Rmd
More on intro and methods

(Current: 880 words. Aim for 650)

  Studies of decision making have consistently associated activity in vmPFC with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Clithero & Rangel, 20??; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011). However, the distributed cortical valuation system also includes posterior cingulate and other mPFC regions, which collectively show significant spatial overlap with the default mode network along the medial wall (DMN; Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011). This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.

  Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions. Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation (Bartra et al., 2010) and DMN (Laird et al., 2009). Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, vmPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena (de la Vega et al., 2016). More specifically, focused work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017). These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same system. However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area (Kragel et al., 2018). While informative, a key limitation in distinguishing constructs through this approach is that meta-analyses often rely on information derived from group-averaged data. Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject. However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret.

  Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI. Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations (Laumann et al., 2015; Gordon et al., 2017; Gratton et al., 2018). Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics (Yeo et al., 2018). In regards to DMN, the trend of individualized analyses has led to finer idiosyncratic subdivisions of the DMN through careful selection of seed-based functional connectivity (Braga & Buckner, 2018). It is thus possible that the indisitinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level. With this in mind, a first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present within mPFC.

  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments (Logothetis, 2008). As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time. Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity (Gordon et al., 2017; Laumann et al., 2015; Tobyne et al., 2018). A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics (Bassett, Zurn, & Gold, 2018). From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018). Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network (Fortunato & Hric, 2016). Among the algorithms used to estimate these communities, modularity has been widely effective in brain networks (Garcia et al., 2018). However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning a more valuable option. In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix). The resulting eigenvector corresponding to the second-to-last eigenvalue (i.e. the Fiedler Vector) provides values to divide the network into a positive and a negative community (Fiedler, 1975). This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.

  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals. This description will allow researchers to generate more precise topographic targets for future studies of decision making. We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data. First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas (Glasser et al., 2013). We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project (HCP; citation), and estimate the extent of DMN coverage through spectral partitioning. The resulting patterns are then evaluated for consistency across methods, throughout each individual's time series, and across subjects.

I'll probably have to fix this in the intro: ADV et al note that dmPFC and vmPFC are more coactivated with DMN's PCC than pregenual ACC. This forms the topological shape that we report here. On my second read, it sounds like my interpretation is still correct: sure, vmPFC coactivates with subcortical value-related areas more than other mPFC sections, but this area also strongly coactivates with DMN in a way that they don't dissect. That's why they talk about the multifaceted embedding of psychological constructs here, even if the subregions they define are part of distinct networks.

@@

With these lists, we computed the number of times every two parcels co-occurred across each literature. This allowed us to generate two weighted networks in which each vertex was a brain parcel, and edges corresponded to the number of times each pair of them co-occurred across studies. Based on this, only edges with co-occurrences higher than 8 were preserved, and the remaining unconnected vertices (brain regions) were discarded. The connectivity strength of every pairwise parcels was then calculated as the sum of their co-occurrences. In order to threshold the parcels that are most likely to belong to each literature, we bootstrapped the connectivity strength and removed edges whose values lied below the 95th percentile of this distribution. In order to select regions of interest (ROI) from mPFC and other brain areas that are central to valuation and DMN literatures, we first bootstrapped the mean strength for each graph separately, and chose areas with strength above the 95th percentile of this distribution. Next, we took the intersection of these areas, such that the final ROIs were brain regions that overlapped between DMN and valuation in the literature (and thus our main target for dissociation).

Next, we identified areas that were solely related to either literature. We limited the search space to the parcels from Glasser et al. (2013) that were contained within the DMN parcellation defined by Yeo et al. (2011). We permuted the label of every study (i.e. DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum statistic from a ROI-wise chi-squared test of proportions on the number of prmuted studies that had reported each ROI. This gave us a null distribution of chi-squared values that was used to determine which ROIs were more significantly prevalent on each literature.

**fMRI Data**
In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state data from the Human Connectome Project (n = 80, randomly sampled from the total pool) Q6 release. Beyond the standard minimally preprocessed pipeline from HCP (), the data went through a number of additional refinements that are detailed elsewhere (Tobyne et al., 2017). Briefly, each dataset was bandpass filtered (DEETS HERE), and had the mean greyordinate signal regressed from every vertex time series (MGSR). Each subject's brain was comprised of 32k vertices per hemisphere. We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject. Resting state data was acquired over four scanning sessions that occurred over the course of two days (two sessions per day). Each resting state scan was comprised of 1200 TRs (TR = 0.720s) for a total time of 14 min 33 s per session. We used this scanning structure to estimate each subject's topology based on session, day, and overall data (4800 TRs).

>>>>

(Current: 942 words. Aim for 650)

  Studies of decision making have consistently associated activity in ventromedial prefrontal cortex (vmPFC) with the subjective value assigned to decision outcomes (Bartra, McGuire, & Kable, 2010; Clithero & Rangel, 20??; Hiser & Koenigs, 2017; Kable & Glimcher, 2007; Levy et al., 2011). However, the distributed cortical valuation system also includes posterior cingulate and more extended mPFC regions, which collectively show significant spatial overlap with the default mode network (DMN) along the medial wall (Fox et al., 2005; Laird et al., 2009; Yeo et al., 2011). This shared neural coverage has prompted the question of whether (and to what extent) these two systems can be dissociated.

  Previous meta-analytic work has provided important insights on the psychological phenomena attributed to mPFC subregions. Independent coordinate-based meta-analyses have found mirroring spatial coverage in mPFC for valuation (Bartra et al., 2010) and DMN (Laird et al., 2009). Whole brain analyses have shown that while more ventral mPFC regions are increasingly associated with reward-related elements of decision making, vmPFC strongly coactivates with DMN regions across the literature, with no clear topographical distinction between these phenomena (de la Vega et al., 2016). More focused meta-analytic work aimed at disentangling DMN from subjective value has determined that these systems are inseparable within mPFC (Acikalin, Gorgolewski, & Poldrack, 2017). These findings highlight the multifaceted embedding of psychological constructs in subregions of mPFC, and suggest that DMN and valuation might indeed be subserved by the same system. However, recent activation-based meta-analytic work has demonstrated considerable domain specificity in this area (Kragel et al., 2018). While informative, a key limitation in distinguishing constructs through this approach is that meta-analyses often rely on information derived from group-averaged data. Averaging has traditionally been beneficial in identifying tendencies in brain function and organization when faced with short scanning sessions per subject. However, it has been shown that mPFC is subject to considerable idiosyncratic cortical folding (Zilles, Palomero- Gallagher, & Amunts, 2013) and inter-subject functional variability (Mueller et al., 2013) compared to the rest of the brain, thus making group-averaging studies difficult to interpret.

  Seeking to remedy these shortcomings, recent work has prescribed relevance to the analysis of single subjects in fMRI. Individual analyses of fMRI data have identified idiosyncratic, reliable, and valid functional organization that would otherwise be blurred in aggregative estimations (Laumann et al., 2015; Gordon et al., 2017; Gratton et al., 2018). Furthermore, subject-specific network arrangements have been found to predict behavioral characteristics (Yeo et al., 2018). In regards to DMN, the trend of individualized analyses has led to finer idiosyncratic subdivisions of the DMN through careful selection of seed-based functional connectivity (Braga & Buckner, 2018). It is thus possible that the indisitinguishable overlap of DMN and valuation effects can be attributed to a lack of spatial resolution that is better understood at the individual level. With this in mind, an important first step in disentangling these phenomena would be to determine the degree of topological heterogeneity of the DMN present within mPFC.

  A persistent issue in analyzing mPFC in individuals is the various factors inducing signal dropout in its more ventral segments (Logothetis, 2008). As such, there is value in examining all possible sources of covariation that compose DMN, instead of estimating topologies one seed at a time. Connectome-based analyses of resting state functional connectivity (rsFC) have been fruitful in characterizing individualized functional topologies that match task-induced activity (Gordon et al., 2017; Laumann et al., 2015; Tobyne et al., 2018). A popular approach to analyze these connectomes is to rely on graph theoretic methods, which provide an organic avenue to understand brain network dynamics (Bassett, Zurn, & Gold, 2018). From these, community detection algorithms have been successfully utilized to section brain networks into cohesive substructures (Garcia, Ashourvan, Muldoon, Vettel, & Bassett, 2018). Such communities represent clusters of network nodes that are more connected with each other than with the rest of the network (Fortunato & Hric, 2016). Among the algorithms used to estimate these communities, modularity has been widely effective in subsectioning brain networks into multiple groups (Garcia et al., 2018). However, in attempting to refine the DMN topology at the individual level, dividing these regions into what belongs and does not belong to DMN makes dissection through spectral partitioning a more valuable option. In short, spectral partitioning performs eigenvalue decompositon on an adjusted form of a correlation matrix (Laplacian matrix). The resulting eigenvector corresponding to the second-to-last eigenvalue (i.e. the Fiedler Vector) provides values to divide the network into a positive and a negative community (Fiedler, 1975). This method can thus capture a refined group of brain regions that more cohesively share activation patterns during rest.

  In this study, we aim to subsection regions commonly attributed to both DMN and subjective value into subject-specific DMN and non-DMN partitions, quantifying the degree of topographical heterogeneity present in this network within and across individuals. This description will allow researchers to generate more precise topographic targets for future studies of decision making. We do this by capitalizing on the respective strengths of meta-analytic and subject-specific analyses of brain data. First, we define regions of interest (ROI) by identifying overlapping activation throughout the literature projected to an established brain atlas (Glasser et al., 2013). We then produce a rsFC networks of all the surface vertices within these ROIs for each individual resting state dataset from the Human Connectome Project (HCP; citation), and estimate the extent of DMN coverage through spectral partitioning. The resulting patterns are then evaluated for consistency across methods, throughout each individual's time series, and across subjects. Finally, we show some interesting properties of SP related to the stability of brain networks.

@@

With these lists, we identified the areas that were more consistently shared between DMN and valuation. For each literature, we summed the number of times each parcel was reported across studies, and performed a one-way chi-squared test of proportions on each parcel with a null probability equivalent to the bootstrapped (5000 iterations) mean of each literature's report counts. In other words, we checked which regions were significantly (p < 0.05) more reported in their respective literatures than their counterparts. Regions of interest were then determined based on which of the remaining regions were common across literatures.

Next, we identified areas that were solely related to either literature. We limited the search space to the parcels that were contained within the DMN parcellation defined by Yeo et al. (2011). We permuted the label of every study (i.e. DMN or valuation) 5000 times while preseving the total number of studies observed in each domain, and on each iteration stored the maximum statistic from a ROI-wise chi-squared test of proportions on the number of prmuted studies that had reported each ROI. This gave us a null distribution of chi-squared values that was used to determine which ROIs were more significantly prevalent on each literature.

**fMRI Data**
In order to quantify the intrinsic connectivity of these ROIs in the brain, we acquired resting-state fMRI data from the Human Connectome Project (HCP; Van Essen et al., 2013; www.humanconnectome.org) Q6 release (n = 80, randomly sampled from the total pool of 469 available subjects). Each subject's data was acquired over two days at Washington University in St. Louis on a Siemens CONNECTOM Skyra MRI scanner (Siemens, Erlangen, Germany). A resting state session (TR = 0.720 s, TE = 33.1 ms, FA = 52°, multiband factor = 8, 72 slices, 2 mm isotropic voxels) was comprised of 1200 TRs for a total time of 14 min 33 s per session, with left-right and left-right phase encoding implemented on each day. We used this scanning structure to estimate each subject's topology based on session, day, and overall data (4800 TRs).

Beyond the in-house minimally preprocessed pipeline from HCP (Glasser et al., 2013), which include motion correction, temporal denoising, highpass filtering (0.0005 Hz threshold), and MNI152 normalization, all scans went through a number of additional refinements (Tobyne et al., 2017). Only subjects with both left-right and right-left phase encoding were included. In addition, only datasets with either low motion levels (under 1.5mm) or 0.5mm mean framewise displacement (FD) were used. Volumes that displayed an FD of over 0.5 mm were considered as spikes and removed from the subject's dataset, and subjects whose spike counts were above 5% of their total data were excluded from analyses. Briefly, each dataset was bandpass filtered (DEETS HERE), and had the mean greyordinate signal regressed from every vertex time series (MGSR). Each subject's brain was comprised of 32k vertices per hemisphere. We retained only the cortical surfaces, which resulted in 59,412 total surface vertices per subject. Resting state data was acquired over four scanning sessions that occurred over the course of two days (two sessions per day).
